Evaluating Model Performances

### 2019-04-02 Scripts/evaluating_model_performances.Rmd
edits to results scripts

>>>>

##gm12878

###none

#OC
##None
rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OC
##None
rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_none <- data.frame(Resolution=rep(c(rep("10 kb", 3),
                                                        rep("25 kb", 3),
                                                        rep("50 kb", 3),
                                                        rep("100 kb", 3)),4),
                                       Predictor=rep(c("OC","OP","Distance"),16),
                                       Metric=c(rep("AUC",12),
                                                rep("F1-Score",12), 
                                                rep("MCC",12),
                                                rep("Balanced Acc", 12)))

all_rfperfs_gm12878_none$Performance <- c(round(rfperf_gm12878_10kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_none_dist[17,2],2), #auc

                                          round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1

                                          round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc

                                          (round(rfperf_gm12878_10kb_none_oc[6,2],2) + round(rfperf_gm12878_10kb_none_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_10kb_none_op[6,2],2) + round(rfperf_gm12878_10kb_none_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_10kb_none_dist[6,2],2) + round(rfperf_gm12878_10kb_none_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_none_oc[6,2],2) + round(rfperf_gm12878_25kb_none_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_none_op[6,2],2) + round(rfperf_gm12878_25kb_none_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_none_dist[6,2],2) + round(rfperf_gm12878_25kb_none_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_none_oc[6,2],2) + round(rfperf_gm12878_50kb_none_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_none_op[6,2],2) + round(rfperf_gm12878_50kb_none_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_none_dist[6,2],2) + round(rfperf_gm12878_50kb_none_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_none_oc[6,2],2) + round(rfperf_gm12878_100kb_none_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_none_op[6,2],2) + round(rfperf_gm12878_100kb_none_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_none_dist[6,2],2) + round(rfperf_gm12878_100kb_none_dist[7,2],2))/2 #balanced accuracy
)

all_rfperfs_gm12878_none$Resolution <- factor(all_rfperfs_gm12878_none$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
all_rfperfs_gm12878_none$Predictor <- factor(all_rfperfs_gm12878_none$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_none$Metric <- factor(all_rfperfs_gm12878_none$Metric, levels = c("AUC",
                                                                                      "Balanced Acc",
                                                                                      "F1-Score",
                                                                                      "MCC"))

p1 <- ggplot(all_rfperfs_gm12878_none,
       aes(x=Resolution, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

###ROS

```{r}
##ROS
rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_ros <- data.frame(Resolution=rep(c(rep("10 kb", 3),
                                                        rep("25 kb", 3),
                                                        rep("50 kb", 3),
                                                        rep("100 kb", 3)),4),
                                       Predictor=rep(c("OC","OP","Distance"),16),
                                       Metric=c(rep("AUC",12),
                                                rep("F1-Score",12), 
                                                rep("MCC",12),
                                                rep("Balanced Acc", 12)))

all_rfperfs_gm12878_ros$Performance <- c(round(rfperf_gm12878_10kb_ros_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_ros_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_ros_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ros_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ros_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ros_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ros_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ros_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ros_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ros_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ros_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ros_dist[17,2],2), #auc

                                          round(rfperf_gm12878_10kb_ros_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_ros_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_ros_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ros_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ros_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ros_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ros_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ros_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ros_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ros_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ros_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ros_dist[16,2],2), #f1

                                          round(rfperf_gm12878_10kb_ros_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_ros_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_ros_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ros_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ros_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ros_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ros_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ros_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ros_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ros_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ros_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ros_dist[15,2],2), #mcc

                                          (round(rfperf_gm12878_10kb_ros_oc[6,2],2) + round(rfperf_gm12878_10kb_ros_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_10kb_ros_op[6,2],2) + round(rfperf_gm12878_10kb_ros_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_10kb_ros_dist[6,2],2) + round(rfperf_gm12878_10kb_ros_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_ros_oc[6,2],2) + round(rfperf_gm12878_25kb_ros_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_ros_op[6,2],2) + round(rfperf_gm12878_25kb_ros_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_ros_dist[6,2],2) + round(rfperf_gm12878_25kb_ros_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_ros_oc[6,2],2) + round(rfperf_gm12878_50kb_ros_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_ros_op[6,2],2) + round(rfperf_gm12878_50kb_ros_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_ros_dist[6,2],2) + round(rfperf_gm12878_50kb_ros_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_ros_oc[6,2],2) + round(rfperf_gm12878_100kb_ros_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_ros_op[6,2],2) + round(rfperf_gm12878_100kb_ros_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_ros_dist[6,2],2) + round(rfperf_gm12878_100kb_ros_dist[7,2],2))/2 #balanced accuracy
)

all_rfperfs_gm12878_ros$Resolution <- factor(all_rfperfs_gm12878_ros$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
all_rfperfs_gm12878_ros$Predictor <- factor(all_rfperfs_gm12878_ros$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_ros$Metric <- factor(all_rfperfs_gm12878_ros$Metric, levels = c("AUC",
                                                                                      "Balanced Acc",
                                                                                      "F1-Score",
                                                                                      "MCC"))

ggplot(all_rfperfs_gm12878_ros,
       aes(x=Resolution, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

###RUS

```{r}
##RUS
rfperf_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_RUS <- data.frame(Resolution=rep(c(rep("10 kb", 3),
                                                        rep("25 kb", 3),
                                                        rep("50 kb", 3),
                                                        rep("100 kb", 3)),4),
                                       Predictor=rep(c("OC","OP","Distance"),16),
                                       Metric=c(rep("AUC",12),
                                                rep("F1-Score",12), 
                                                rep("MCC",12),
                                                rep("Balanced Acc", 12)))

all_rfperfs_gm12878_RUS$Performance <- c(round(rfperf_gm12878_10kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_dist[17,2],2), #auc

                                          round(rfperf_gm12878_10kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_dist[16,2],2), #f1

                                          round(rfperf_gm12878_10kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_dist[15,2],2), #mcc

                                          (round(rfperf_gm12878_10kb_RUS_oc[6,2],2) + round(rfperf_gm12878_10kb_RUS_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_10kb_RUS_op[6,2],2) + round(rfperf_gm12878_10kb_RUS_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_10kb_RUS_dist[6,2],2) + round(rfperf_gm12878_10kb_RUS_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_RUS_oc[6,2],2) + round(rfperf_gm12878_25kb_RUS_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_RUS_op[6,2],2) + round(rfperf_gm12878_25kb_RUS_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_RUS_dist[6,2],2) + round(rfperf_gm12878_25kb_RUS_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_RUS_oc[6,2],2) + round(rfperf_gm12878_50kb_RUS_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_RUS_op[6,2],2) + round(rfperf_gm12878_50kb_RUS_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_RUS_dist[6,2],2) + round(rfperf_gm12878_50kb_RUS_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_RUS_oc[6,2],2) + round(rfperf_gm12878_100kb_RUS_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_RUS_op[6,2],2) + round(rfperf_gm12878_100kb_RUS_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_RUS_dist[6,2],2) + round(rfperf_gm12878_100kb_RUS_dist[7,2],2))/2 #balanced accuracy
)

all_rfperfs_gm12878_RUS$Resolution <- factor(all_rfperfs_gm12878_RUS$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
all_rfperfs_gm12878_RUS$Predictor <- factor(all_rfperfs_gm12878_RUS$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_RUS$Metric <- factor(all_rfperfs_gm12878_RUS$Metric, levels = c("AUC",
                                                                                      "Balanced Acc",
                                                                                      "F1-Score",
                                                                                      "MCC"))

ggplot(all_rfperfs_gm12878_RUS,
       aes(x=Resolution, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

###SMOTE

```{r}
##SMOTE
rfperf_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_SMOTE <- data.frame(Resolution=rep(c(rep("10 kb", 3),
                                                        rep("25 kb", 3),
                                                        rep("50 kb", 3),
                                                        rep("100 kb", 3)),4),
                                       Predictor=rep(c("OC","OP","Distance"),16),
                                       Metric=c(rep("AUC",12),
                                                rep("F1-Score",12), 
                                                rep("MCC",12),
                                                rep("Balanced Acc", 12)))

all_rfperfs_gm12878_SMOTE$Performance <- c(round(rfperf_gm12878_10kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_SMOTE_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_dist[17,2],2), #auc

                                          round(rfperf_gm12878_10kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_SMOTE_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_dist[16,2],2), #f1

                                          round(rfperf_gm12878_10kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_SMOTE_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_dist[15,2],2), #mcc

                                          (round(rfperf_gm12878_10kb_SMOTE_oc[6,2],2) + round(rfperf_gm12878_10kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_10kb_SMOTE_op[6,2],2) + round(rfperf_gm12878_10kb_SMOTE_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_10kb_SMOTE_dist[6,2],2) + round(rfperf_gm12878_10kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_SMOTE_oc[6,2],2) + round(rfperf_gm12878_25kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_SMOTE_op[6,2],2) + round(rfperf_gm12878_25kb_SMOTE_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_25kb_SMOTE_dist[6,2],2) + round(rfperf_gm12878_25kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_SMOTE_oc[6,2],2) + round(rfperf_gm12878_50kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_SMOTE_op[6,2],2) + round(rfperf_gm12878_50kb_SMOTE_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_50kb_SMOTE_dist[6,2],2) + round(rfperf_gm12878_50kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_SMOTE_oc[6,2],2) + round(rfperf_gm12878_100kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_SMOTE_op[6,2],2) + round(rfperf_gm12878_100kb_SMOTE_op[7,2],2))/2, #balanced accuracy
                                          (round(rfperf_gm12878_100kb_SMOTE_dist[6,2],2) + round(rfperf_gm12878_100kb_SMOTE_dist[7,2],2))/2 #balanced accuracy
)

all_rfperfs_gm12878_SMOTE$Resolution <- factor(all_rfperfs_gm12878_SMOTE$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
all_rfperfs_gm12878_SMOTE$Predictor <- factor(all_rfperfs_gm12878_SMOTE$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_SMOTE$Metric <- factor(all_rfperfs_gm12878_SMOTE$Metric, levels = c("AUC",
                                                                                      "Balanced Acc",
                                                                                      "F1-Score",
                                                                                      "MCC"))

ggplot(all_rfperfs_gm12878_SMOTE,
       aes(x=Resolution, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

##k562

###none

#OC
##None
rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OC
##None
rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

all_rfperfs_K562_none <- data.frame(Resolution=rep(c(rep("10 kb", 3),
                                                        rep("25 kb", 3),
                                                        rep("50 kb", 3),
                                                        rep("100 kb", 3)),4),
                                       Predictor=rep(c("OC","OP","Distance"),16),
                                       Metric=c(rep("AUC",12),
                                                rep("F1-Score",12), 
                                                rep("MCC",12),
                                                rep("Balanced Acc", 12)))
